\documentclass[11pt]{letter}
\usepackage{ifthen}
\usepackage{times}
\usepackage{graphics}

\textwidth 6.5in
\textheight 9in
\headheight 0in
\headsep 0in
\topmargin 0.0in
\evensidemargin 0in
\oddsidemargin 0in

\raggedright

\newcommand{\place}{your university}
\newcommand{\thecustom}{}
\newcommand{\custom}[2]{\renewcommand\place{#1}\renewcommand\thecustom{#2}}

\newboolean{skiprobin} 
\setboolean{skiprobin}{false}

\makelabels

\address{Larry D. Pyeatt, PhD\\2624 Dana\\Lubbock, Texas 79415\\(806)763-0577}
\begin{document}

\signature{Larry D. Pyeatt, PhD}



\custom{UMR}{%\enlargethispage{-\baselineskip} 
Although I have been granted tenure and promotion at Texas Tech, I am highly
motivated to move to Rolla.  When I finished my PhD in 1999, I was invited
to UMR for an interview. UMR was at the top of my list for desirability.
However, due to financial constraints, UMR cancelled my interview.  UMR is
still a very desirable place for me, and my daughter and ex-wife have
already relocated there.  I have secured a six-month visiting professor
position in the ECE department at UMR, and will be co-teaching a course with
Don Wunsch on Markov Decision Processes during the Spring 2005 semester.
Since I will already be on campus, an interview would be very inexpensive.

My research interests in AI and robotics complement those of some of your
current faculty members. In addition, over the past year, I have begun work
to apply probabilistic AI in the field of bioinformatics.  The first task
was to bring myself and some of my students up to speed in the
bioinformatics field.  We have done that and have identified some potential
applications.  We are just beginning our explorations.  I am preparing a
grant proposal which I expect to submit in Spring or Summer of 2005.
}
\begin{letter}{Human Resource Services\\
Reference Number:  00032217/00031009\\
University of Missouri-Rolla\\
1202 North Bishop\\
1870 Miner Circle\\
Rolla, MO 65409-1050}
\opening{Dear search committee,}
\input{cover_letter_body}
\closing{Sincerely,}
\end{letter}



\end{document}