%    * Communication skills (oral and written)
%    * Teamwork/group/interpersonal skills
%    * Leadership skills
%    * Work-ethic traits, such as drive, stamina, effort, self-motivation, diligence, ambition, initiative, reliability, positive attitude toward work
%    * Logic, intelligence, proficiency in field of study

%Please consider my application for the position of assistant professor.  

I am writing to apply for a faculty position in the Computer Science
 department at UMR.  My record
shows that I am the type of person you need.  I am an excellent teacher and
researcher and would make a valuable addition to your faculty.

\thecustom

My record at Texas Tech shows that I would bring a proven ability to perform
research and attract funding.  I have developed an active research program
and created the AI Robotics Lab at Texas Tech.  I have been involved in
writing several proposals for funded research projects.  I have always
worked in a collaborative setting.  I believe that my ability to attract
funding and collaboration would be valuable at \place.

I enjoy teaching and find it to be rewarding.    Course evaluations
indicate that the students view me as an excellent, though demanding,
instructor.  My background in computer science is broad and I can teach a
wide range of courses from introductory programming to advanced theory.  I
bring industry experience to the classroom and focus on theory and skills
that will help the students throughout their careers.  My strong teaching
ability would be an asset to \place.

My record of departmental service is also good.  As graduate advisor, I
re-structured the graduate program to increase graduate student enrollment
and improve graduate student quality.  As a result of my efforts, our PhD
enrollment increased from four PhD students in 1999,
to twenty-four in 2002, and over thirty in 2004.
%Other departmental service includes coaching the ACM programming team,
%serving on graduate and undergraduate curriculum committees, leading the
%computer and network, steering committee, serving on the faculty searchthe CS 
%committee, and serving as interim system administrator.
While performing a high level of departmental service, I have also been
active outside the department, serving as reviewer for journals and
conferences, and serving on the program committees. My
involvement in service activities could benefit the department at \place.

I have enclosed my curriculum vitae, a statement of teaching and research
interests, and evidence of teaching and research effectiveness.  I have also
asked my referees to send letters of recommendation.  Please contact me at
(806)763--0577 (home), or by e-mail at {\verb!pyeatt@cs.ttu.edu!} if you
require any additional information.  My web page at
\verb!http://www.cs.ttu.edu/~pyeatt!  always has links to the most recent
version of my curriculum vitae and a broad sample of my research papers. The
AI robotics lab web page at \verb!http://www.cs.ttu.edu/robot!  gives an
overview of my current research efforts.  I look forward to hearing from
you.



%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "cover_letter"
%%% End: 
