%    * Communication skills (oral and written)
%    * Teamwork/group/interpersonal skills
%    * Leadership skills
%    * Work-ethic traits, such as drive, stamina, effort, self-motivation, diligence, ambition, initiative, reliability, positive attitude toward work
%    * Logic, intelligence, proficiency in field of study

%Please consider my application for the position of assistant professor.  

You need an technical lead who will work diligently with the existing staff
to advance your research and development missions.  My record shows that I
am the type of person you need.  I am an excellent researcher and a strong
team player.  I could contribute a great deal to \place.

I was a resident expert in artificial intelligence at Texaco.  During
my employment there I successfully converted technology from the 
research stage into practical systems.  Earlier in my industrial 
career, I lead teams in designing custom control systems.  My job
was to envision the high-level architectures, communicate them
to the team members, divide responsibilities between team members,
and work closely with each person to ensure that potential problems
were caught early and corrected.  My leadership skills and AI 
domain knowledge are what you need at \place.

I have a great deal of software development experience, particularly in C
and C++, and  I am able to quickly produce correct code.
%While performing my dissertation research, I wrote about 45,000
%lines of C++ code.  I have made small contributions to the Linux kernel and
%to other open source projects.  At Texaco I wrote the SpectraMan package,
%which was about 35,000 lines of C++ code.  While working at Applied
%Hydraulics, I became proficient in several flavors of Assembly language. 
As a student, I was on the ACM programming team that placed third in the
international programming competition.  
%I have written several large
%software packages for courses, including a 9000 line ray-tracing package and
%an 11,000 line optimizing compiler.  
My coding skills would be a big benefit to \place.

%I have developed an active research program and created the AI Robotics Lab
%at Texas Tech. Now in its second year of operation, the lab has already
%produced three MS theses and three conference publications.  
At Texas Tech, I have been involved in writing proposals for funded research
projects totaling over \$2M.  I have always worked in a collaborative
setting, and have continuing collaborative research efforts with Adele Howe
at Colorado State University and several people at NASA and here at Texas
Tech.  I believe that my ability to attract funding and collaboration would
be valuable at \place.

I have enclosed my curriculum vitae, including references, and
I would be happy to discuss salary requirements when I hear
from you.
Please contact me at (806)763--0577 (home), (806)239--1001
(cell), or by e-mail at {\verb!pyeatt@cs.ttu.edu!} if you require any
additional information.  My web page at
\verb!http://www.cs.ttu.edu/~pyeatt!
always has links to the most recent version of my curriculum vitae and a
broad sample of my research papers. The AI robotics lab web page at
\verb!http://www.cs.ttu.edu/robot! gives an overview of my current
research efforts.  I look forward to hearing from you.



%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "cover_letter"
%%% End: 
