

My main research interests are probabilistic AI techniques and mobile
robot navigation in complex unstructured environments.  My most recent
work deals with robust control and learning for partially observable,
uncertain, and non-stationary environments, and using machine learning
techniques to control sedation of surgical patients.  My research
interests can be divided into three general areas:
\begin{description}
\item[Probabilistic Techniques:] I am investigating partially
  observable Markov decision process (POMDP) techniques.  My research
  in this area is aimed at efficiently finding exact and approximate
  policies for POMDP problems.  So far, the application domain for
  this work has been autonomous mapping and navigation of indoor
  environments.  My next goal is to extend the current techniques to
  work in large outdoor environments. Outdoor robotics pose several
  grand challenges in the area of mobile robotics.

\item[Sensor Modeling:]
 In order to use the probabilistic mapping techniques, it is necessary to
 convert a stream of sensor data into a stream of local maps.  Data from
 multiple local maps, possibly generated from different sensors, can be
 fused to form a global map.  For some sensors, such as laser and sonar,
 the sensor model is well understood and easy to implement.  However, no
 good model for stereo vision exists.

\item[Learning Actions:] The behaviors that humans perform are quite
  often either completely reflexive or were learned at an early age
  and have since become reflexive in nature. Higher level behaviors
  are ordered sets of these sub-cognitive behaviors. I am very
  interested in developing solutions for learning these low-level
  sub-cognitive behaviors in order to provide them to intelligent
  agents for ordering in high-level behaviors. For my dissertation
  work, I developed a framework for using POMDP based navigation with
  reinforcement learning (RL) to provide adaptive low-level actions.
  This work was a proof of concept and was done completely in
  simulation.  Some of my current work is aimed at extending the
  architecture to run on a real robot.
\end{description}

My future research plans involve continued effort in learning and
control, and application of probabilistic techniques in domains other
than robotics.  In particular, I am interested in applying
probabilistic machine learning techniques in healthcare and clinical
settings. I have also begun investigating distributed computing and
adaptive wireless networks to support computation and communication
between computers, sensors, and robots.  I would also enjoy working on
issues of human-robot interaction, including gesture recognition,
learning through imitation, and understanding high-level spoken
commands.

