\documentclass[11pt]{resume}
\usepackage{ifthen}
\usepackage{times}
\usepackage{fancyheadings}

\textwidth 7.25in
\evensidemargin -0.375in
\oddsidemargin -0.375in
\topmargin -0.25in
\textheight 9.5in

\newboolean{prospectus} 
\setboolean{prospectus}{false}

\leftcolwidth{1in}
\colsep{0.1in}
\outdent{0.25in}
\outdent{0in}
 
\headheight 3\normalbaselineskip
\headsep \normalbaselineskip
\addtolength{\topmargin}{-3\normalbaselineskip}
\addtolength{\textheight}{-1\normalbaselineskip}
\lhead{}
\rhead{\thepage}
\chead{Larry D. Pyeatt, PhD\\Curriculum Vitae}
\cfoot{}
\lfoot{}
\rfoot{}

\begin{document}
\name{\begin{minipage}{\textwidth}\vspace*{-\baselineskip}\begin{center}Larry D. Pyeatt, PhD \\ Curriculum Vitae\end{center}\end{minipage}}

\pagestyle{fancyplain}
\thispagestyle{empty}

\address{2624 West Dana \\ Lubbock, Texas 79415 \\ (806) 763--0577\\
         pyeatt@cs.ttu.edu }
\line


\section{Education}
  {Doctor of Philosophy in Computer Science}
  {\\Colorado State University, 1999 \\
  Dissertation:  {\it Integration of Partially Observable Markov
Decision Processes and Reinforcement Learning for Simulated Robot 
Navigation}\\ 
  Committee: Adele Howe (Chair), Charles Anderson, 
  Darrell Whitley, Wade Troxell }
   
\section{} 
  {Master of Science in Computer Science}    
  {\\Texas Tech University, 1991 \\
  Thesis:   {\it Application of the Neural Ring Pattern Classifier
  to Speech Recognition}\\
  Committee: W. J. Bryan Oldham (Chair), Thomas M. English, Donald Gustafson}
   
\section{} 
  {Bachelor of Science in Computer Science}    
  {\\Texas Tech University, 1988 \\
  Minor in Psychology with additional course work in Mathematics and 
  Electrical Engineering}

\section{Research Interests}  
  {}
  {Partially Observable Markov Decision Processes,
   Reinforcement Learning, Function Approximation, Robotics and
   Agent Architectures, Real-time and Embedded Systems }

\section{Honors and Awards}  
{Academic}   
{\\
Upsilon Pi Epsilon (computer science honor society), Texas Tech University,
1989\\
Third Place Team, ACM International Programming Competition,
Louisville, Kentucky,  1989\\
President's List, Texas Tech, Spring 1986 \\
Dean's List, Texas Tech, Multiple times \\
Engineering Academic Scholarship, Texas Tech University, 1983}

\section{}
{Texaco}   
{\\Patent Letter, August 30, 1995\\
Patent Application Award, July 19, 1993 \\
Exploration \& Production Technology Department Award for 
Outstanding Supplier, February 23, 1993  \\
Individual Outstanding Contribution (IOC) Award for Innovation,
August 5, 1992}

%\section{Languages}
%{}{English, Russian}



\section{Professional Experience}
{Assistant Professor} {Texas Tech University, Lubbock, 9/99--present.
  Served as graduate advisor and was responsible for re-structuring and
  improving the Master's and Doctoral programs.  Currently focusing on
  research in Robotics, Partially Observable Markov Decision Processes, and
  Reinforcement Learning.  Taught several graduate and undergraduate
  courses including courses in digital logic, operating systems,
  reinforcement learning, and artificial intelligence.  Received very high
  student evaluations without sacrificing high student performance
  expectations.  Directed research work of several MS students
  and one undergraduate.}

\section{}
{Lecturer}{Colorado State University,
  Fort Collins, 9/98--9/99. Taught courses in digital
  logic and assembly language, operating systems, and programming
  languages.}
% Explored several areas of AI before focusing on
%  reinforcement learning and partially observable Markov decision processes
%  in the context of robotics for my dissertation. Taught courses in digital
%  logic and assembly language, operating systems, and programming
%  languages.}

\section{}
{Graduate Research Assistant}{Colorado State University, Fort Collins,
  multiple appointments, 9/93--9/98.  Research in areas of partially
  observable Markov decision processes, robotics, neural networks and
  reinforcement learning, finding structure in discrete event sequences,
  geographical information systems (GIS), and genetic algorithms.
 The following sections detail some of the research that 
  I conducted at Colorado State.}
      \begin{description}
      \item[Partially Observable Markov Decision
        Processes](9/97--9/99)
        \ Implemented several POMDP solution
        algorithms. 
        Extended  the Incremental Pruning algorithm and code to perform
        distributed execution on a cluster UNIX machines.
      \item[Robotics] (9/97--9/99)
        \ Developed a three-level control architecture for a mobile robot
        using a symbolic planner at the highest level, POMDP planning at
        the middle level, and reinforcement learning
        at the low level.  Implemented middle and low levels and
        demonstrated that a robot could learn low level
        extended actions
        as necessary to complete its task and could modify its low level
        actions to adapt to sensor  and effector failures.
      \item[Neural Networks and Reinforcement Learning](9/96--9/97)
        \ Experimented with reinforcement
        learning using neural networks for function
        approximation.  Ran experiments using a Pente simulator, pole-balancing
        simulator, and the Robot Auto Racing Simulator (RARS).  Added a 
        high-level controller to the RARS system to allow switching between
        learned behaviors.  Invented a new function approximation
        technique based on decision trees.  Showed that it was superior to
        the neural network approach.
      \item[Structure in Discrete Event Sequences](9/95--9/97)
        \ Developed method to detect dependencies in program execution traces
        and construct a Semi-Markov model of the underlying system behavior.
        Worked with Adele Howe, Eric Dahlman
        and Gabriel Somlo to write CLASPWeb, which allows anyone with a web
        browser to use the code. %(http://satchmo.cs.colostate.edu:4936)
      \item[Geographical Information Systems (GIS)](5/95--8/95)
        \ Developed method to normalize lighting and remove shadows 
        from aerial and satellite terrain photographs.  The software
        worked by texture mapping the photograph onto the corresponding
        USGS elevation data, calculating the position of the sun at the
        time the photograph was taken, and applying an inverse lighting
        calculation.  The normalized photograph could then be texture mapped
        onto the USGS elevation data and a forward lighting model could
        be applied to show lighting conditions at any time of day and year.
      \item[Genetic Algorithms](9/93--5/95)
        \ Developed system to 
        track the ranking of hyperplanes during genetic search;
        compared dynamic ranking with static ranking.
        Wrote code to evolve neural network weights. Compared the
        results with Fr\'ed\'eric Gruau's Cellular Encoding method.  
%      \item[Other projects]
%        Completed several smaller projects, including a ray tracer,
%        a computer vision system, and an optimizing compiler for a language
%        similar to C.
\end{description}


\section{}
    {Senior Information Systems Programmer} {Texaco Inc., Houston 
      9/91--9/93.  Applied  Artificial
    Intelligence techniques to Texaco business needs.
  Delivered applications on PC, Unix, and IBM
    mainframe platforms.  Performed system administration for Unix
    environment.  Used a wide variety of systems, languages, tools,
    and techniques.
 Major projects were:}
\begin{description}
\item[SpectraMan](9/92--9/94) \ Ultraviolet Fluorescence Spectra Manager.
  The software was used to automate the process of identifying and
  characterizing unknown hydrocarbon mixtures. The chemist could use a
  neural network, embedded in the software, to match an unknown sample to
  every other sample in the database.  The neural net selected a
  user-specified number of similar spectra that the chemist could then view
  and print along with additional information in the database.  Based on the
  similar samples, the chemist could then determine the characteristics of
  the unknown sample.  This software greatly reduced the time required to
  perform an analysis and enabled a large increase in the productivity of
  the chemists.  The software was written in C using the X Window System,
  Motif, OpenGL, and an SQL database server.  It was developed on Sun and
  delivered on SGI.  The lead chemist, Dr. Marilyn Reyes, and I were awarded
  United States Patent 5424959.
   
 \item[Reservoir Modeling Expert System](11/9--11/92) \ The reservoir
   management team at Texaco gathers production data on every reservoir that
   Texaco owns.  Once they have sufficient data on a particular reservoir,
   they try to fit the data to one of several mathematical models.  If they
   select the correct model, they can accurately predict the production of
   the reservoir and select an appropriate production schedule.  There were
   very few people experienced in selecting the model, and several experts
   had recently retired or were preparing to retire. The team leader was
   faced with having an inexperienced staff and no one to train them.  I
   built an expert system for selecting the reservoir model, allowing the
   team to continue its work with a reduced and less experienced staff.
\end{description}
   
 \section{}
  {Graduate Research Assistant}
   {Texas Tech University, Lubbock,  8/88--9/91. Research
  in neural networks and speech recognition.}
\begin{description}
      \item[Speech Recognition] Developed speaker independent speech
      recognition system for digits.  The speech recognition system
      followed the now standard model of signal preprocessing, fast
      Fourier transform, Mel scale extraction, segmentation using a
      hidden Markov model, and recognition.  The recognition section
      used a neural ring pattern classifier.  
      \item[Embedded Control] Evaluated hardware and
      operating systems for embedded distributed control of silicon
      wafer processing machinery.  Made recommendation to the
      company that funded the study.  Taught Introduction to
      Computer Science course using Pascal.  Taught digital
      electronics lab.  Supervised construction of circuits by the
      students.  Assisted students in the implementation of their
      circuit designs.  \end{description}

%\section{}{Self-Employed}{8/88--7/89. 
%      Developed accounting and subscriber list software for small newspapers. 
%      Wrote code in C and Pascal on IBM PC and Apple Macintosh systems.}
   
\section{}{Embedded Control Systems Engineer} {Applied
  Hydraulics, Lubbock, Texas, 1/87--7/88.  Designed and built
  microprocessor and sequential logic based systems for industrial control
  and data acquisition. 
  Designed circuit boards for the systems.
  Supervised technical staff who were responsible for constructing
  the hardware designs.  Designed and wrote software for the new
  systems in assembly and C.  Supervised for all stages of
  the process: assessing customer needs, creating design
  specifications, implementing the systems, installing at the
  customer's site, and providing post-delivery technical
  assistance.}



%\pagebreak

\newcommand{\bibfile}{/home/faculty2/pyeatt/bibliography/complete}



%%%%%\pagebreak
%\enlargethispage*{\baselineskip}
\begin{citations}{Journal Articles}{\bibfile}
\nocite{Pyeatt:Howe:J00}
\end{citations}

\begin{citations}{Articles in Preparation}{\bibfile}
\nocite{Pyeatt:J03}
\nocite{Pyeatt:Ellore:J03}
\nocite{Pyeatt:Bansal:J03}
\nocite{Pyeatt:Kona:J03}
\end{citations}

\begin{citations}{Conference Papers}{\bibfile}
\nocite{pyeatt2003a}
\nocite{quasny2003a}
\nocite{Moore:Quasny:Pyeatt:Sinzinger:C01b}
\nocite{Pyeatt:Howe:C01a}
\nocite{Pyeatt:Howe:C99c}
\nocite{Pyeatt:Howe:C99a}
\nocite{Pyeatt:Howe:C98b}
\nocite{Pyeatt:Howe:C98a}
\nocite{Howe:Pyeatt:C96}
\nocite{Gruau:Whitley:Pyeatt:C96}
\nocite{Whitley:Gruau:Pyeatt:C95}
\nocite{Whitley:Mathias:Pyeatt:C95}
\nocite{Pyeatt:Oldham:C91}
\end{citations}

%\begin{citations}{Papers in Preparation}{\bibfile}
%\nocite{Pyeatt:Quasny:C03}
%\nocite{Moore:Quasny:Pyeatt:C03}
%\end{citations}

 
%\begin{citations}{Doctoral \\ Dissertation}{\bibfile}
%\nocite{PyeattTHESIS}
%\end{citations}

%\begin{citations}{Master's \\ Thesis}{\bibfile}
%\nocite{Pyeatt:91}
%\end{citations}

\begin{citations}{Unrefereed Symposia \&
Workshops}{\bibfile}
\nocite{Pyeatt:Howe:WS99a}
\nocite{Pyeatt:Howe:FS98}
\end{citations}

\begin{citations}{Unrefereed Technical Reports}{\bibfile}
\nocite{Stevens:Pyeatt:Houlton:Goss:95}
\nocite{Pyeatt:Howe:TR98c}
\end{citations}

\begin{citations}{Professional
Presentations}{\bibfile}
\nocite{Present02a}
\nocite{Present01b}
\nocite{Present01a}
\nocite{Present00a}
\nocite{Present99c}
\nocite{Present99b}
\nocite{Present99a}
\nocite{Present98c}
\nocite{Present98b}
\nocite{Present98a}
\nocite{Present97}
\nocite{Present96}
\nocite{Present91}
\end{citations}

\begin{citations}{Patent}{\bibfile}
\nocite{Reyes:Pyeatt95}
\end{citations}


\begin{citations}{Grants}{\bibfile}
\nocite{GrantC}
\nocite{GrantA}
\nocite{GrantB}
\end{citations}

\begin{citations}{Pending Proposals}{\bibfile}
\nocite{GrantProposalD}
\nocite{GrantProposalJ}
\end{citations}

%\begin{citations}{Proposals in Preparation}{\bibfile}
%\nocite{GrantProposalE}
%\nocite{GrantProposalF}
%\nocite{GrantProposalG}
%\end{citations}

%\begin{citations}{Unsuccessful Proposals}
%{\bibfile}
%\nocite{GrantProposalB}
%\nocite{GrantProposalA}
%\nocite{GrantProposalH}
%\nocite{GrantProposalI}
%\end{citations}

%Progress}{\bibfile}
%\nocite{PyeattTHESIS}
%\nocite{PyeattWIPa}
%\nocite{PyeattWIPb}
%\nocite{PyeattWIPc}
%\nocite{PyeattWIPd}
%\end{citations}


\section{Departmental Service}{}
{Coached Programming Team 1999--2002\\
  Developed System Administrator Guidelines for the CS department network\\
  Developed System Usage Policies for the CS department network\\
 Served as graduate advisor 2000--2001\\
\hspace*{1em} Re-structured the degree requirements for MS degree\\
\hspace*{1em} Created new forms and procedures to improve consistency and help enforce requirements\\
\hspace*{1em} Worked to improve consistency in admissions\\
\hspace*{1em} Developed new leveling requirements and created mechanisms to ensure compliance\\
\hspace*{1em} Instituted policies that encourage students to take the thesis option\\
\hspace*{1em} Drove the creation of posters and brochures to recruit graduate students\\
Improved the quality of our computer systems support\\
\hspace*{1em} Configured server to provide more reliable service\\
\hspace*{1em} Installed numerous software packages on server and clients\\
\hspace*{1em} Set up accounts for all students enrolled in CS courses\\
\hspace*{1em} Provided email lists for faculty, staff, and students\\
\hspace*{1em} Set up web-based system support request forms\\
\hspace*{1em} Provided systems support to other
faculty, staff, and students\\
Organized the UIL Computer Science competition at Texas Tech\\
Served on faculty recruiting comittee, 2001-2002\\
Served on several M.S. thesis comittees
}

\section{Professional Service }{Reviewer}
        {\\
2002 IASTED International Conference on Applied Informatics (AI 2003)\\
2001 IEEE Transactions on Pattern Analysis and Machine Intelligence\\
2001 International Symposium on Adaptive Systems\\
2000 IEEE Transactions on Pattern Analysis and Machine Intelligence \\ 
1999 Journal of Experimintal and Theoretical Artificial Intelligence\\
1999 IEEE Transactions on Knowledge and Data Engineering\\
\rm
1998 American Journal of Mathematical and Management Sciences\\
}

\section{\ }{Program Committee}
        {\\
2001 Third International Syposium on Adaptive Systems \\
}




\section{Courses Taught}{Undergraduate}
{\\
\hspace*{1em} Advanced Digital Projects\\
\hspace*{1em} Operating Systems\\
\hspace*{1em} Introduction to AI Robotics\\
\hspace*{1em}  Programming Languages\\
\hspace*{1em} Introduction to Digital Logic\\
\hspace*{1em} Introduction to Computer Science
}

\section{}{Graduate}
{\\
\hspace*{1em} Reinforcement Learning\\
\hspace*{1em} Advanced Operating Systems\\
\hspace*{1em} Intelligent Systems\\
\hspace*{1em} Introduction to AI Robotics\\
\hspace*{1em} All-terrain Robotics
}

\section{Students Advised}{Master's Students}
{\\Srividya Kona, graduated in May, 2002\\
  Ajay Bansal, graduated in May, 2002\\
  Bharani Ellore, graduated in December, 2002\\
  Todd Quasny, expected graduation in May, 2004
}

%\section{}{Bachelor's Students}
%{\\Todd Quasny, graduated in December, 2001
%}

%\section{Languages \& Systems }{}
%        {C, C++, Pascal, Modula-2, Modula-3, PL/1, Lisp,    
%        Prolog, Ada, LISP, 8051 assembly, 80x86 assembly, 
%        VAX Macro assembly, IBM 360 assembly, 680x0 assembly, 
%        6811 assembly, MIPS assembly, Unix, Macintosh, X11, Motif, 
%        Athena, SQL, Perl, HTML, OpenGL, Java. }
%\pagebreak

%\section{References}{}{Available upon request}
\section{References}{Adele E. Howe,}{(advisor) Department of Computer
  Science, Colorado State University, Fort Collins, CO 80523.  Telephone:
  (970) 491--7589 Email: howe@cs.colostate.edu}

\section{}{Eric D. Sinzinger,}{(co-worker) Department of Computer Science, 
  Texas Tech University, Box 43104, Lubbock, TX 79409. Telephone: (806)
  742--3527 Email: sinzinge@cs.ttu.edu}

\section{}{Henry Hexmoor,}{(colleague) Department of Computer Science 
  \& Computer Engineering, University of Arkansas, Engineering Hall, Room 328
  Fayetteville, AR 72701.  Telephone: (479) 575--2420
  Email: hexmoor@uark.edu }

\section{}{Todd M. Quasny,}{(student) Department of Computer Science,
  Texas Tech University, Box 43104, Lubbock, TX 79409.  Telephone: (806)
  438--8633 Email: todd@quasny.com}


\ifthenelse{\boolean{prospectus}}
{\newpage
%\setcounter{page}{1}

\name{\begin{minipage}{\textwidth}\vspace*{-\baselineskip}\begin{center}Larry
D. Pyeatt \\ Statement of Research Interests \end{center}\end{minipage}}

\address{1228 Columbine Court \\ Fort Collins, CO 80521 \\ (970) 490--6047\\
         pyeatt@cs.colostate.edu \\ Available May, 1999}

\line
\setlength\parskip{\baselineskip}
\setlength\parindent{1em}
\thispagestyle{empty}
\chead{Larry D. Pyeatt \\ Research Interests}
\input{research-body}
\newpage
%\setcounter{page}{1}

\name{\begin{minipage}{\textwidth}\vspace*{-\baselineskip}\begin{center}Larry
D. Pyeatt \\ Statement of Teaching Interests \end{center}\end{minipage}}

\address{1228 Columbine Court \\ Fort Collins, CO 80521 \\ (970) 490--6047\\
         pyeatt@cs.colostate.edu \\ Available May, 1999}

\line
\setlength\parskip{\baselineskip}
\setlength\parindent{1em}
\thispagestyle{empty}
\chead{Larry D. Pyeatt \\ Teaching Interests}
\input{teaching-body}
}{}

\end{document}

